Data Processing

### 2020-01-24 analysis/data_processing.Rmd
add first model for age

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(psych)
library(readODS)

@@

```{r}
# importing data
### die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
files <- dir("~/Work/PragBat/raw_data/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,33,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date, 
                                               trial = as.character(trial))
  raw_data <- bind_rows(raw_data, id)
}

unique(raw_data$subid)

task_data <- raw_data %>%
  filter(trial != "training", 
         trial != "filler1", 
         trial != "filler2",
         trial != "train",
         trial != "train2")%>%
  filter(phase == "shape" | is.na(phase))%>%
  mutate(subid = recode(subid, `13.2` = "Vp13.2",
                        `13.2` = "Vp13.2",
                        `14.2` = "Vp14.2",
                        `16.2` = "Vp16.2",
                        `19.1` = "Vp19.1",
                        `12.1` = "Vp12.1",
                        `29.2` = "Vp29.2",
                        `26.1` = "Vp26.2",
                        `37.1` = "Vp37.1",
                        `38.1` = "Vp38.1"
                        ))%>%
  select(subid, subage, test_date, task, trial, correct)%>%
  separate(subid, into = c("id","test_day"), sep="\\.")%>%
  mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))

@@

task_data <- read_csv("../data/data.csv")

@@

log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
  mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
         id = paste("Vp",`ID `, sep = ""))%>%
  select(id, age, status)

data <- task_data %>%
  left_join(log)%>%
  mutate(check_age = ifelse(subage == substr(age,1,1),T,F))

@@

```{r}
p1 <- data%>%
  group_by(id,subage,task)%>%
  filter(subage != "5",
         task != "training")%>%
  summarise(mean = mean(correct))

@@

ggplot(data = p12, aes(x = age, y = mean))+
  geom_hline(yintercept = .5, lty = 2)+
  geom_jitter(alpha = .5, width = .2, height = .01)+
  geom_smooth(method = "glm")+
  facet_wrap(~task)+
  labs(x = "Age", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  theme_few()+
  theme(legend.position = c(.85,.2))
```

@@

```{r}
reli <- data%>%
  filter(task != "training")%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

@@

```{r}
reli_age <- data%>%
  filter(task != "training")%>%
  group_by(subage, id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(subage,task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

@@

```{r}
cor <- data%>%
  filter(task != "training")%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = reli$reli)%>%
  gather(task, cor, -rowname)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()

>>>>

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
library(psych)
library(readODS)
library(brms)

@@

```{r}
# importing data
### die flogenden Zeilen kannst du überspringen. Weiter gehts in Zeile 68
# files <- dir("~/Work/PragBat/raw_data/")
# 
# raw_data <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/PragBat/raw_data/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,33,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date, 
#                                                trial = as.character(trial))
#   raw_data <- bind_rows(raw_data, id)
# }
# 
# unique(raw_data$subid)
# 
# 
# task_data <- raw_data %>%
#   filter(trial != "training", 
#          trial != "filler1", 
#          trial != "filler2",
#          trial != "train",
#          trial != "train2")%>%
#   filter(phase == "shape" | is.na(phase))%>%
#   mutate(subid = recode(subid, `13.2` = "Vp13.2",
#                         `13.2` = "Vp13.2",
#                         `14.2` = "Vp14.2",
#                         `16.2` = "Vp16.2",
#                         `19.1` = "Vp19.1",
#                         `12.1` = "Vp12.1",
#                         `29.2` = "Vp29.2",
#                         `26.1` = "Vp26.2",
#                         `37.1` = "Vp37.1",
#                         `38.1` = "Vp38.1"
#                         ))%>%
#   select(subid, subage, test_date, task, trial, correct)%>%
#   separate(subid, into = c("id","test_day"), sep="\\.")%>%
#   mutate(test_day = ifelse(id == "Vp12" & test_date =="2019-11-26", 2, test_day))

@@

#task_data <- read_csv("../data/data.csv")

@@

# log <- read_ods("../../VP Liste.ods", sheet = 2)%>%
#   mutate(age = as.numeric(difftime(test_day_1, `birthday `, units = "days"))/365.25,
#          id = paste("Vp",`ID `, sep = ""))%>%
#   select(id, age, status)
#   
# 
# data <- task_data %>%
#   left_join(log)%>%
#   mutate(check_age = ifelse(subage == substr(age,1,1),T,F))

data <- read_csv("../data/data.csv")%>%
  mutate(subage = factor(subage),
         trial = ifelse(test_day == "2", trial + 4, trial))%>%
  select(-X)

@@

```{r}
p1 <- data%>%
  group_by(id,subage,task)%>%
  filter(task != "training")%>%
  summarise(mean = mean(correct))

@@

ggplot(data = p12, aes(x = age, y = mean))+
  geom_hline(yintercept = .5, lty = 2)+
  geom_jitter(alpha = .5, width = .2, height = .01)+
  geom_smooth(method = "glm")+
  facet_grid(~task)+
  labs(x = "Age", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  theme_few()+
  theme(legend.position = c(.85,.2))+
  coord_fixed(ratio = 2)
```
# Card Sorting model

```{r}
# card sorting

card_sorting_data <- data %>%
  filter(task == "card_sorting")

card_sorting_model_data <- card_sorting_data %>%
  mutate(age = age - mean(age),
         trial = trial - mean(trial))

# card_sorting_model1 <- brm(correct ~ age + trial + (trial|id),
#                     data = card_sorting_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4, 
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/card_sorting_model1.rds")
# 
# card_sorting_model2 <- brm(correct ~ trial + (trial|id),
#                     data = card_sorting_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4, 
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/card_sorting_model2.rds")

card_sorting_model1 <-readRDS("../saves/card_sorting_model1.rds")

card_sorting_model2 <-readRDS("../saves/card_sorting_model2.rds")

ts <- loo_compare(card_sorting_model1, card_sorting_model2, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, card_sorting_model1 = "correct ~ age + trial + RE", 
                   card_sorting_model2 = "correct ~ trial + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)

ts

summary(card_sorting_model1)

```{r}
p_sum_cs1 <- card_sorting_data %>%
  mutate(subage = as.numeric(as.character(subage)))%>%
  group_by(age,subage,id) %>%
  summarise(correct = mean(correct))

p_sum_cs2 <- p_sum_cs1 %>%
  group_by(subage) %>%
  multi_boot_standard(col = "correct")

samples_cs_1 <- posterior_samples(card_sorting_model1, "^b")%>%
  mutate(sample = 1:length(b_age))

samples_cs_2 <- expand_grid(samples_cs_1,card_sorting_model_data$age)%>%
  mutate(y = plogis(b_Intercept + b_age * `card_sorting_model_data$age`),
         age = `card_sorting_model_data$age` + mean(card_sorting_data$age),
         experiment = "card_sorting")%>%
  filter(sample < 1000)

map_cs <- tibble(
  age = card_sorting_model_data$age,
  int = fixef(card_sorting_model1)[1,1],
  slope = fixef(card_sorting_model1)[2,1]
)%>%
  mutate(y = plogis(int + slope * age),
         age = age + mean(card_sorting_data$age_num))

p_cs <- ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples_cs_2, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = map_cs, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_sum_cs1,aes(x = age, y= correct), width = .00, height = .01, alpha = .5)+
  geom_pointrange(data = p_sum_cs2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  scale_color_manual(values = "#CC6677")
```

@@

```{r}
reli <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

@@

```{r}
reli_age <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(subage, id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(subage,task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

@@

```{r}
cor <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = reli$reli)%>%
  gather(task, cor, -rowname)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()
